Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-01-30 docs/ACM/paper.tex
Adding discussion about cost model.

%% Packages that we are using in this version of the work:
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{paralist}

@@

>>>>

%% Packages that we are using in this version of the work:
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{paralist}
\usepackage{mathpartir}

@@

% Explain the tension between large and small tasks.
The benefit of creating tasks depend on two factors:
runtime cost, and parallelism.
These two factors lead to a sweet spot in the size of tasks, where size is
measured as the amount of code they contain.
The smaller the tasks are, the more parallel they tend to be, as a consequence
of less dependencies.
However, if tasks are too small, then the performance gained by the extra
parallelism might not be enough to pay for the cost of managing them.
On the other hand, if tasks are too big, then we might not obtain enough
parallelism, because individual tasks still execute sequentially.
In this paper, we extract the smallest thread above the runtime cost.
To bestow meaning into this last statement, in what follows we define more
formally the notions of task size and runtime cost.

\paragraph{Estimating the Size of Tasks.}
The size of a task is given by its workload, i.e., the number of instructions that
such task executes.
The same program region might lead to the creation of tasks with different sizes.
Therefore, the actual size of a task is only known after the threads finishes
execution.
However, to judge if the creation of a task is worth its cost, we must be able to
approximate its size statically.
With this goal, we define the notion of static workload estimate:

\begin{definition}[Static Workload Estimate (SWE)]
\label{def:swe}
Let $G = G_1 \cup G_2 \cup \ldots \cup G_n$ be a partition of a program's control
flow graph $G$ into $n$ {\em maximal} hammock regions.
We define the static workload estimate ($W(G)$) as a real number, such that
$W(G) = W(G_1) + W(G_2) + \ldots + W(G_n)$.
\end{definition}

\begin{figure}[t!]
\begin{small}
\begin{eqnarray*}
\begin{tabular}{lc}
\mbox{(Instruction)} &
W(\mbox{instr}) = 1
\\\\
\mbox{(Sequence)} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2}{W(S_1;S_2;) = w_2}
\\\\
\mbox{(Branch)} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ W(S_3) = w_3}
{W(\mbox{if}(S_1) \ S_2; \ \mbox{else} \ S_3;) = w_1 + w_2 + w_3}
\\\\
\mbox{(Unknown Lp)} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = \mbox{?}}
{W(\mbox{while} (S_1) \ S_2;) = 10 \times (w_1 + w_2)}
\\\\
\mbox{(Known Loop)} &
\inferrule{W(S_1) = w_1 \\ W(S_2) = w_2 \\ X(S_1) = E}
{W(\mbox{while} (S_1) \ S_2;) = E \times (w_1 + w_2)}
\end{tabular}
\end{eqnarray*}
\end{small}
\caption{\label{fig:swe}Estimating the cost of tasks.}
\end{figure}

% Explain how we use symbolic information to compute costs.

% Discuss the expansion algorithm.
\paragraph{The Task Expansion Algorithm.}
